PineAPPL: combining EW and QCD corrections\\ for fast evaluation of LHC processes

### 2020-10-26 paper/answer_to_the_editor.txt

Dear Editor,

We would like to thank the referee for carefully reading the manuscript and
making useful comments and suggestions.

For convenience all changes are marked in the pre-compiled document as
red/strikethrough (removed text) and blue/underlined (added text).

@@

In the following our answers to the issues raised by the referee:

- Issues 1, 3, 4, 5, 6, 8, 9, and 11 have all been addressed as suggested, or
  corrected otherwise.
- Issue 2: The decomposition of the fixed-order expansion written down in eq.
  (2.1) holds to all orders in both the strong and electroweak coupling, and
  therefore the mentioned sentence is correct, as it only concerns PineAPPL.
  The Monte Carlo that we used is limited to NLO, of course.
- Issue 7: For Drell-Yan we checked that a dynamical scale set to Mll does
  change the NLO QCD in the largest invariant mass bins and therefore also the
  scale uncertainty. In comparison to the shown data uncertainty the changes
  are very minor, and therefore we did not update plots and text.
  For the Z transverse momentum process we did update the both plots and text,
  where we indeed see a significant increase of the scale variation band in
  the large transverse momentum bins. The electroweak corrections are also
  smaller, since we normalise to NLO QCD.
- Issue 10: A brief discussion on this matter has been added at the beginning
  of section 3. The reference suggested (Buccioni:2020cfi), is cited in section 
  3.2.1, in the discussion relevant for Drell-Yan.
- Issue 12: Although we agree with the referee that the mentioned tables are
  interesting only to a few readers, the main text refers to it in a few
  places and therefore removing it from the main document would require bigger
  changes. We see no harm in leaving the tables in the document and therefore
  decided to keep them.

### 2020-10-26 paper/sec-introduction.tex
Add final changes to the text

In the second respect, contemporary PDF
sets~\cite{Harland-Lang:2014zoa,Ball:2017nwa,Hou:2019efy}
incorporate a significant amount of LHC data, which is analysed with NNLO QCD 
theory by default. No EW corrections are systematically included in the 
theoretical description of the experimental observables to which PDFs are 
optimised, except for QED effects if a photon PDF is 
determined~\cite{Martin:2004dh,Ball:2013hta,Schmidt:2015zda,Manohar:2016nzj,Manohar:2017eqh,Bertone:2017bme,Harland-Lang:2019pla}. The QED contribution is
included in the matrix element (at the lowest order for the LHC
processes considered) and in the DGLAP splitting
functions at leading order~\cite{Bertone:2013vaa}. Inclusion of NLO QCD--QED
combined corrections in the evolution is in principle also
possible~\cite{deFlorian:2015ujt}, and should be required to analyse the data
within consistent pertubatibe accuracy if higher-order EW and QCD corrections
are also included in partonic cross sections.
The resulting relative PDF uncertainty --- which accounts only for the
uncertainty of the data and of residual methodological inefficiencies inherent to 
each PDF determination --- can be as low as \SI{1}{\percent} at the EW
scale~\cite{Ball:2017nwa}. Theoretical uncertainties, possibly of comparable 
size (e.g.\ from missing higher-order terms in the QCD perturbative
expansion), have started to be represented 
into PDF uncertainties only very 
recently~\cite{AbdulKhalek:2019bux,AbdulKhalek:2019ihb}.

>>>>

In the second respect, contemporary PDF
sets~\cite{Harland-Lang:2014zoa,Ball:2017nwa,Hou:2019efy}
incorporate a significant amount of LHC data, which is analysed with NNLO QCD 
theory by default. No EW corrections are systematically included in the 
theoretical description of the experimental observables to which PDFs are 
optimised, except for QED effects if a photon PDF is 
determined~\cite{Martin:2004dh,Ball:2013hta,Schmidt:2015zda,Manohar:2016nzj,Manohar:2017eqh,Bertone:2017bme,Harland-Lang:2019pla}. The QED contribution is
included in the matrix element (at the lowest order for the LHC
processes considered) and in the DGLAP splitting
functions at leading order~\cite{Bertone:2013vaa}. Inclusion of NLO QCD--QED
combined corrections in the evolution is in principle also
possible~\cite{deFlorian:2015ujt}, and should be required to analyse the data
within consistent perturbative accuracy if higher-order EW and QCD corrections
are also included in partonic cross sections.
The resulting relative PDF uncertainty --- which accounts only for the
uncertainty of the data and of residual methodological inefficiencies inherent to 
each PDF determination --- can be as low as \SI{1}{\percent} at the EW
scale~\cite{Ball:2017nwa}. Theoretical uncertainties, possibly of comparable 
size (e.g.\ from missing higher-order terms in the QCD perturbative
expansion), have started to be represented 
into PDF uncertainties only very 
recently~\cite{AbdulKhalek:2019bux,AbdulKhalek:2019ihb}.
